% pull in our defines
\input{./defines.tex}

% singlespace this section
\singlespace

\paragraph{Project Journal}
\begin{description}
\item[9/14/13] Team members and leaders established.
\item[9/17/13] Team name determined: \emph\teamName.
\item[9/25/13] HTML5 established as our primary development language.
\item[10/01/13] Emailed the client regarding:
    \begin{enumerate}
        \item Bootstrap by Twitter usage
        \item Cover page requirements
    \end{enumerate}
\item[10/01/13] Answer received to the email on 10-01-13.
\item[10/03/13] Emailed the client regarding:
    \begin{enumerate}
        \item Interface drawing requirements
        \item CSS and JavaScript usage
    \end{enumerate}
\item[10/06/13] Interface drawing completed. Scheduled meeting to complete the UML diagram.
\item[10/08/13] UML diagram completed. Statement of issues encountered, resolutions, and 
                what is to be accomplished by the next reporting period completed.
\item[10/15/13] General meeting discussing the distribution of work to be done on the website.
\item[10/22/13] Met with the Project Manager after class and discussed our first progress report.
\item[10/24/13] First session of coding. 
\item[10/26/13] Second session of coding. 
\item[11/02/13] Meeting discussing how the site is progressing and if any major design changes to
                be implemented.
\item[11/08/13] Short programming session.
\item[11/14/13] General meeting discussing individual/website status. 
\end{description}
