\documentclass[12pt,oneside]{article}

% pull in our defines
\input{./defines.tex}

% pull in our layout
\input{./layout.tex}

\begin{document}

% pull in our title page
\input{./title.tex}

% add our title, name, and members to the top page
\begin{center}
{\large\bf \projectTitle \\ ~\\}
{\teamName: \\\teamMembers}
\end{center}

% pull in our journal
\input{./journal.tex}

\doublespace
\paragraph{Introduction}
\hfill \\
Included within this progress report are the Interface Drawing and the UML
Class Diagram for the student web-based enrollment system.
\singlespace

\paragraph{Issues and Resolutions}
\begin{enumerate}
    \item Disagreements upon the overall design and features.
        \begin{enumerate}
            \item Worked together in a friendly give-and-take environment until everyone was
                  satisfied with the final product/draft.
        \end{enumerate}
    \item Abstract User class while creating the UML diagram.
        \begin{enumerate}
            \item We decided that only students would need to access the system.
            \item As such, we didn't need a base User class for which Students,
                  Teachers, and potentially Administrators would be derived.
        \end{enumerate}
    \item Time conflicts and constraints
        \begin{enumerate}
            \item Created a blocked schedule that clearly defined the times each member was
                  unavailable to meet.
            \item Used the blocked schedule to create meeting times.
        \end{enumerate}
\end{enumerate}

\paragraph{Deliverables for Next Report}
\begin{enumerate}
    \item Implement our interface based on the designs and UML.
    \item Create a rough draft of our presentation.
    \item Create a rough draft of our final report.
\end{enumerate}

% make sure we single-space the bibliography
\singlespace

% our bibliography
%\input{./bib.tex}

\end{document}
