\documentclass[12pt,oneside]{article}

% pull in our defines
\input{./defines.tex}

% pull in our layout
\input{./layout.tex}

\begin{document}

% pull in our title page
\input{./title.tex}

% add our title, name, and members to the top page
\begin{center}
{\large\bf \projectTitle \\ ~\\}
{\teamName: \\\teamMembers}
\end{center}

% pull in our journal
\input{./journal.tex}

\doublespace
\paragraph{Introduction}
\hfill \\
Included within this progress report are the updated Interface Drawing and UML
Class Diagram for the student web-based enrollment system.
\singlespace

\paragraph{Issues and Resolutions}
\begin{enumerate}
    \item Our Use Case Diagram was not created correctly in the first progress report.
        \begin{enumerate}
            \item The Use Case Diagram was re-done correctly and included in Progress Report II.
        \end{enumerate}
    \item Disputes the color scheme of the website.
        \begin{enumerate}
            \item Ongoing discussions about what colors we'd like to include.
        \end{enumerate}
    \item Learning the version control system.
        \begin{enumerate}
            \item Spending time on Github and helping each other figure out how to use it
                  efficiently and effectively.
        \end{enumerate}
    \item Time conflicts/constraints.
        \begin{enumerate}
            \item Worked together with everyone's schedule to arrange meeting times where everyone
                  will be available.
        \end{enumerate}
\end{enumerate}

\paragraph{Deliverables from Last Report}
\begin{enumerate}
    \item Implemented our design.
    \item Created a first draft presentation.
    \item Met with the Project Manager.
\end{enumerate}

\paragraph{Deliverables for Next Report}
\begin{enumerate}
    \item Create and finalize project presentation.
    \item Create and finalize project report.
    \item Finalize color scheme and add finishing touches to the system.
    \item Submission of final project.
\end{enumerate}

% make sure we single-space the bibliography
\singlespace

% our bibliography
%\input{./bib.tex}

\end{document}
